---
title: "Immigration, Gender, and Doctoral Dreariness"
author: "Aramis D. M. Valverde"
date: "12/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Is It Perhaps Different Doing A PhD In A Country You Grew Up In As Opposed to One That You Moved To? Is Nature Good At Doing Surveys?
## I Mean, Probably Yes to Both Those Questions, But I Dont Know, So Lets Find Out!



## Abstract:



A 2019 Nature survey of doctoral students worldwide conducted by Shift Learning, [a UK based education market research and consulting firm](https://www.shift-learning.co.uk/), demonstrated that PhD students are not doing all that well. The Nature [write up by Chris Woolston](https://www.nature.com/articles/d41586-019-03459-7) noted that more than a third of PhD students have sought help for anxiety or depression caused by their their PhD studies, and more than a fifth of PhD students had experienced discrimination or harassment in their PhD program. Prior research has backed up the concept that PhD students, and graduate students at large, aren't doing terribly well. As a PhD student I thought, "yeah, I feel it, its pretty bad, I'm pretty sad.". However I reassured myself that at least I didn't have to deal with being an actual immigrant or a woman. But then one asks oneself, "huh, is it actually worse? Maybe Bill O'Rielly was right when he said that women don't experience discrimination in the workplace.".

To analyze if it is worse to be a PhD student and a woman, or a gender queer/ non binary person, or an immigrant, as opposed to not those things, I analyzed Nature's data set as published on [figshare](https://figshare.com/articles/dataset/Nature_Graduate_Survey_2017/5480716?file=9558301). The analysis took the form of an exploratory data analysis, where many different avenues of discourse were attempted and ideated. I also analyzed the history of the data, its transformations, its chain of custody, and the limitations and problems that the data set may present with.


```{r someVar,results='hide', echo=FALSE,include=FALSE}
#Sorry, misc. relevant links. These are hidden in the output of the paper as some of these havent been used in it, and therefore will be irrelevant as they havent been cited. Still, they remain here for posteriority.(And because I may refer to them later in a more thurough write up and analysis of this dataset)
#https://group.springernature.com/gp/group/media/press-releases/archive-2019/nature-phd-survey-puts-spotlight-on-mental-health/17372858
#https://www.zmescience.com/other/pieces/journals-to-blame-poor-phd-mental-health-0432/
#https://www.insidehighered.com/news/2019/11/14/phd-student-poll-finds-mental-health-bullying-and-career-uncertainty-are-top
#https://www.nature.com/articles/d41586-019-03535-y
#https://figshare.com/articles/dataset/Data_publication_survey_raw_data/1234052
#https://figshare.com/articles/dataset/Nature_Graduate_Survey_2017/5480716?file=9558301
#https://www.nature.com/articles/nj7677-549a

#https://phys.org/news/2019-11-nature-phd-survey-spotlight-mental.html
#https://www.nature.com/articles/d41586-021-01538-2
#https://www.apollo.io/people/Karen/Kaplan/54a7df517468696b7f4ceb54
#https://laptrinhx.com/news/interview-with-karen-kaplan-senior-careers-editor-at-nature-E3OYqY5/
```

## Introduction:

Things are hard for PhD students. Research has demonstrated a persistent and severe toll on the mental health of PhD students due to the conditions that they are put under. More than a third have sought help for anxiety and depression caused by their PhD studies, and a fifth of PhD students have experienced discrimination and harassment in their program. A [2020 study of UK PhD students](https://onlinelibrary.wiley.com/doi/abs/10.1002/capr.12437?__cf_chl_jschl_tk__=2NIUSjRMyi_VDwOrxUtn3r60rXsjnFQeqsrPfr6T7pI-1639471304-0-gaNycGzNCH0) found that 40 percent of said students were at high risk of suicide, with 8 percent having made an attempt.

That being said, every doctoral student's experience is not the same. Some student's experiences are worse. U.S. based doctoral students originating from China also have to deal with [isolation, loneliness, and alienation](https://eric.ed.gov/?id=EJ1133943). Some trans students have to deal with severe hostility or insensitivity related to their gender identity or expression, leading suicide attempts rates [four times higher than trans students who did not have that severe experience](https://psycnet.apa.org/record/2012-27680-006). It is therefore very unfortunate that this survey lumped transgendered and cisgendered people into one variable. Erasure, especially in research, has [consequential and damaging effects on trans people](https://www.sciencedirect.com/science/article/abs/pii/S1055329009001071).Gender queer and non-conforming was included, so I will attempt an analysis. However, people identifying as such were few, so I may not be able to demonstrate a significant difference even if one is liable to exist. It is also important to note that gender-specific [approaches yield more accurate results, contribute to lessening the paucity of trans research, and are considered best practice](https://www.liebertpub.com/doi/full/10.1089/trgh.2020.0054).

I must note that I am a minority doctoral student myself. While I am a minority in my department and in my country, I am not an immigrant, nor am I a minority in the state or city where I am studying (Merced, California). I struggle with no language barrier, no one chides me for my voice, and I can travel freely throughout my campus and the city I reside in. I note this because, while my analysis of the data stands on its own, my identity is such that I am not able to speak from direct experience, and that is a limitation within this work.

I was lead to this data set by a [tidytuesday post on github](https://github.com/rfordatascience/tidytuesday/issues/153), and this research was completed as the final assignment for Dr. Dan Hicks' [data science methods course](https://data-science-methods.github.io/project/) at UC Merced. The data set used in this analysis was sourced from [this figshare page](https://figshare.com/s/74a5ea79d76ad66a8af8).


## Methods


### An Analysis of The Data's History 

#### Nature Careers and Shift Insight

Nature has had a survey of doctoral students conducted every two years for ten years. The latest survey, conducted in 2019, was advertised by Nature in its "Career News" section, and was titled, "Nature calling: take our PhD survey". This survey was conducted by an English corporation by the name of Shift Insight. Shift Insight is the owning and operating body of Shift Learning, Shift Sustainability, and Shift Membership https://shift-insight.co.uk/about-shift-insight/. This corporation is owned by [Jane Powell](https://www.linkedin.com/in/jenny-kedros-3074471a/), a former Publisher at Pearson and Palgrave Macmillan. Shift Insight mainly performs [market research](https://shift-insight.co.uk/research-reports-and-blogs/), however as with the Nature survey they also conduct public facing research for large institutions. Most staff at Shift Insights have a marketing, writing, or publishing background.

#### A Faliure to Protect Privacy and Anonymity

Their website's language seems to [demonstrate commitments to data security](https://shift-insight.co.uk/quality-and-values/), however these amount to either declarations of compliance strictly within the confines of the law, or membership with non-binding commerce and industry associations. Unfortunately for participants, Nature Careers and Shift Insight failed to remove all personally identifying information, specifically the emails of two students and the names of two others, according to my own analysis, where I found two names and emails, along with sensitive and possibly damaging information which was attributable to those persons.

#### A Non-Tidy Data Set

While working with the data I discovered that the excel sheet that was used was not prepared for easy analysis on mediums other than excel itself. In R, the excel sheet holding the data was difficult to work with, requiring the renaming by hand of many columns, the removal of empty columns, the combination of columns that could have been mutually exclusive, and a naming scheme that was less than helpful. Due to the formatting and naming conventions used by the researchers, troubleshooting the importation and use of the data took up far more time than the analysis itself. 

#### The Chain of Command at Shift

The finance director and data compliance officer is the person responsible for ensuring that sensitive data is adequately handled. At Shift, that person is Jack Wilson. [Jack Wilson](https://www.linkedin.com/in/jack-wilson-0751853/) appears to have no credentials to handle sensitive data, unlike some of his [co-workers](https://shift-insight.co.uk/about-shift-insight/#our-team), and seems to have been educated at "LAMBDA", without any named degree, according to their linkedin profile. While I could not locate a university by the name of LAMBDA, it is possible that this education was associated with a fraternal organization,and it is also quite possible that Jack Wilson graduated with that education at the top of their class, albeit without a degree. I mention this not just because I want to dunk on these people, but rather because their seemingly irresponsible handling of data could have some real consequences for those people who have had their data exposed. I also mention credentials because Shift appears to have existed for 20 years but has only had moderately to mildly credentialed persons on staff for [seven years](https://www.linkedin.com/search/results/people/?currentCompany=%5B%222294535%22%5D&origin=COMPANY_PAGE_CANNED_SEARCH&sid=3Ve). The only visible doctorate holder entered the company on [November 2021](https://www.linkedin.com/in/daisy-alero-emoekabu-phd-b22b2319/). This, along with the founders' recent certification and education in R may help explain why the data arrived in a state that was not in line with tidy data principles, why proper attention was not paid to anonymization, and why the analysis of the data was relatively limited. The [privacy statement](https://shift-insight.co.uk/privacy-policy/), limited as it was, may have also been broken by the lack of proper anonymization.

#### The Line of Custody
The data appears to have passed through the hands of at least three people, [Elsie Lauchlan](https://www.linkedin.com/in/elsie-lauchlan-990276a3/), the primary researcher for the analysis, [David Payne](https://www.linkedin.com/in/david-payne-0a681013/?originalSubdomain=uk), The managing editor at Careers and Supplements at Nature Springer, and [Karen Kaplan](https://www.linkedin.com/in/karen-kaplan-03186b9/), the senior editor of Nature's careers section. According to the version control sheet in the survey script titled "Nature_GradSurvey_Script2019_Final1.docx", there were four versions of the analysis or survey. That is very few given the scope and size of the survey, however it is possible that further analysis could have been forsaken due to cost, as the same paper notes that additional changes may involve extra costs.

#### Limitations
First and foremost I must mention that this data set and the conclusions that have been drawn from it thus far have necessarily been influenced by the funder of the study itself, Nature Careers. While those at Nature Careers may state impartiality or that they do not interfere where there is a conflict of interest, it is important to note that the very focus of the survey itself is guided by those who fund it. If I pay for a survey of cake market share, I may not be pleased when I am delivered instead an analysis of carcinogens in cakes, with my cake factory winning in an evaluation of "most carcinogens per pound-cake". This, is of course not a novel idea. Dr. Federico Germani at University of Zurich, however, took this critique a step further. His analysis and survey demonstrated that [most PhD students rate "publishing in high impact journals" as the factor contributing most to their general stress level](https://www.zmescience.com/other/pieces/journals-to-blame-poor-phd-mental-health-0432/). The possibility of this analysis downplaying or misrepresenting the publisher's role in PhD student unhappiness is exacerbated not only by the the journal's funding and control over the project, but also by the fact that the survey was advertised by a big, high impact journal, Nature. The connection to the journal Nature was so strong in fact, that some students seemed to erroneously believe that Nature was conducting the survey, further tainting the participant's ability to directly point the finger at publishers at large.

Second is the fact that the data has been cleaned to an extent that has not been disclosed by shift insights. The amount of anonymization and the methods of cleaning the data from the vendor or software that was used to produce the data is not fully and clearly disclosed. Because of this we have no way of discerning what was removed or how the data was manipulated. I also could not attempt the ordinal survey, as the [link had expired](https://wh1.snapsurveys.com/s.asp?k=162210914288&s=article it does appear to have been conducted through Snapsurveys.comhttps://www.snapsurveys.com/survey-software/pricing/). The issue of unusual cleaning is exemplified by noting that the "Name" column, which appears to be based on when the individual finished the survey, starts at 1 and ends at 9839. This wouldn't be odd, except that the survey has only 6812 rows. To remove nearly a third of the data set may be justified, however the spacing of these deletions is odd. For instance, until row 349 in the excel sheet, we see no removals have occurred, then at row 350 we have lost our first batch of participants, as the number which has been increasing one by one suddenly jumps up from 347 at line 349 to 356 at 350. Moreover, By line 373 we have jumped all the way to 779. In 24 rows, from 349-373, we have lost 376 individuals! This is not to say that anything suspicious is going on, but rather this is meant to illustrate that we simply cannot properly evaluate what has happened to these values and therefore we cannot evaluate if the loss of those values could have impacted their or our subsequent analysis in any way. 


Third is the fact that the participant pool is liable to have been skewed because of the method of advertisement (via Nature Careers), and because Shift Insights seems to reuse [participants](https://shift-insight.co.uk/respondent-faqs/). This survey was also used to recruit to their participant pool, as evidenced by the question towards the end of the survey asking for contact information and asking if the participant would like to be included in later surveys. Because of their commercial interests and [focus on market research](https://shift-insight.co.uk/research-reports-and-blogs/), it is possible that their existing participant pool is incidentally selecting against and for some traits. For example, I am not liable to read to an email from Shift Insight, much less participate in their surveys, because I don't respect market researchers. This selection bias may be partially mitigated against by the fact that some PhD students appear to have thought that Nature was conducting the survey, and not Shift Insights. Some students responded as if the people conducting the survey had some sort of authority, one attempted to report their superiors, another asked for help publishing in Nature.

Fourth is the fact that the survey was only conducted in five languages. Persons from parts of the world who communicate in languages that aren't English, Portuguese, Spanish, Chinese, or French are not likely to have responded to the survey, even if they are competent in the language. 

Fifth is a lack of representation. There is little mention or analysis possible for non cis-gendered persons, and there is no capacity for me to make a gender specific analysis of the data as mentioned prior. There is also the issue that persons from certain countries were not given the option to select their country. Taiwan made up the vast majority of write in answers for country of origin in Asia. The point is that overall the survey could do a bit more to provide more specific data, even if in their own analysies they bunch data points up into groups, as with Asia, Australasia, Europe, etc.

Finally, we have the issue that these are self reported data and that that participants may have wanted to introduce their own positive self perceptions. Some participants may have had some concerns about putting this information in a website for fear that their comments may make them identifiable. For at least four students, these sorts of concerns were certainly warranted. The participants may have also wanted to present themselves in a positive light more generally. Given the doctoral community is more than a little neurotic, there are a myriad of manners by which this data could have been skewed by the use of self report measures and not direct measures.



## Findings
### Immigration
#### As Defined, Immigration Does Not Have as Large of A Consequence as Gender, But This May Be a Consequence of an Inadequate Definition
<br>
I found that 






## Code and Analysis



In this section I go about creating the graphs and the cursory analysis that is the bulk of this paper.

To hide the whole bit: {r ,results='hide', echo=FALSE,include=FALSE}
To run but not output the results: {r echo = T, results = 'hide', message=FALSE, warning=FALSE}
Load in Libraries and Installations
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
library(tinytex)
library(RColorBrewer)
library(ggdist)
library(waffle)
library(dplyr)
```
Here I load in data set that I downloaded from the link above(and which I placed into a "data" folder within the project folder) and check that it imported properly
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
# I downloaded this data from:  
# https://figshare.com/articles/dataset/Nature_Graduate_Survey_2017/5480716?file=9558301, 
# then placed it into a new folder, christened with the poetic title, "data'.
dfog <- read_excel("data/Nature_PhD survey_Anon_v1.xlsx")
```
Glimpse was used to help ensure that it all was imported properly
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
glimpse(dfog)
```
Head was used to check that the top line had been preserved.
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
head(dfog)
```

The spreadsheet had been loaded in successfully, and it was used to create the data frame, named "dfog", I would analyze and clean. dfog stands for "data frame original".

<br>

### DATA WRANGLIN' AN' CLEANIN' For Use Later On

<br>

<br>

Here I created some ancillary data frames, sf1,df2, and df3, that could be used later to ensure that no accidental changes had been made.
```{r}
df1 <- dfog
df2 <- df1 
df3 <- df2 
```

Here I did some data cleaning by removing the very top row and then using the second row (the questions themselves) as the column's identifiers. The semicolons and periods in the top row created many issues in r, mainly by making the name appear to be a funciton and making the use of packages like dplyr nearly impossible to use.
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
df4 <- df3
names(df4) <- as.matrix(df4[1, ])
df4 <- df4[-1, ]
df4[] <- lapply(df4, function(x) type.convert(as.character(x)))
```

Here I remove all columns where all values are NA
```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
df5 <- df4
df6a <- df5[ , colSums(is.na(df4)) < nrow(df4)]
```

I rename columns that currently have the same name, as that causes issues. I also rename column 117's name in df6a, because the column name in that position is blank. I am not sure how the bottom portion works with attributing df6 to df6a after I declared df6, but it does. I tried it other ways and it didn't output df6. To test this, please do comment out df6 <- df6a and test yourself. I use this work flow to rename all repeated bits, because doing it any other way wouldn't work. Dplyr's tools didn't work for renaming either, and renaming was only accomplished with base r.

```{r echo = T, results = 'hide', message=FALSE, warning=FALSE}
df6 <- df6a

###AV Note: Column name/question is sourced from Nature_GradSurvey_Script2019_Final1.docx.
df6 <- names(df6a)[117] <- "How much do you expect your PhD to improve your job prospects?"     


###AV Rename all duplicates of "If other, please specify" and make unique
df6 <- names(df6a)[12] <- "specified1" 
df6 <- names(df6a)[16] <- "specified2" 
df6 <- names(df6a)[22] <- "specified3" 
df6 <- names(df6a)[34] <- "specified4" 
df6 <- names(df6a)[37] <- "specified5" 
df6 <- names(df6a)[54] <- "specified6" 
df6 <- names(df6a)[79] <- "specified7" 
df6 <- names(df6a)[89] <- "specified8"
df6 <- names(df6a)[104] <- "specified9" 
df6 <- names(df6a)[116] <- "specified10" 
df6 <- names(df6a)[139] <- "specified11" 
df6 <- names(df6a)[141] <- "specified12" 
df6 <- names(df6a)[146] <- "specified13" 
df6 <- names(df6a)[158] <- "specified14" 
df6 <- names(df6a)[173] <- "specified15" 
df6 <- names(df6a)[183] <- "specified16" 
df6 <- names(df6a)[191] <- "specified17" 
df6 <- names(df6a)[200] <- "specified18"
df6 <- names(df6a)[225] <- "specified19" 
df6 <- names(df6a)[233] <- "specified20" 
df6 <- names(df6a)[239] <- "specified21" 
df6 <- names(df6a)[255] <- "specified22" 
df6 <- names(df6a)[261] <- "specified23"

###AV Rename all duplicates of "What prompted you to study outside your country of 
#upbringing" and make unique
df6 <- names(df6a)[23] <- "prompt to study outside country of upbringing1" 
df6 <- names(df6a)[24] <- "prompt to study outside country of upbringing2" 
df6 <- names(df6a)[25] <- "prompt to study outside country of upbringing3" 
df6 <- names(df6a)[26] <- "prompt to study outside country of upbringing4" 
df6 <- names(df6a)[27] <- "prompt to study outside country of upbringing5" 
df6 <- names(df6a)[28] <- "prompt to study outside country of upbringing6" 
df6 <- names(df6a)[29] <- "prompt to study outside country of upbringing7" 
df6 <- names(df6a)[30] <- "prompt to study outside country of upbringing8" 
df6 <- names(df6a)[31] <- "prompt to study outside country of upbringing9" 
df6 <- names(df6a)[32] <- "prompt to study outside country of upbringing10" 
df6 <- names(df6a)[33] <- "prompt to study outside country of upbringing11" 

###AV Rename all duplicates of "Who was the perpetrator(s)" and make unique
df6 <- names(df6a)[97] <-  "positionOfPerpetrator1" 
df6 <- names(df6a)[98] <-  "positionOfPerpetrator2" 
df6 <- names(df6a)[99] <-  "positionOfPerpetrator3" 
df6 <- names(df6a)[100] <- "positionOfPerpetrator4" 
df6 <- names(df6a)[101] <- "positionOfPerpetrator5" 
df6 <- names(df6a)[102] <- "positionOfPerpetrator6" 
df6 <- names(df6a)[103] <- "positionOfPerpetrator7" 

###AV Rename all duplicates of "Which of the following have you experienced?" 
#and make unique
df6 <- names(df6a)[107] <- "experience1" 
df6 <- names(df6a)[108] <- "experience2" 
df6 <- names(df6a)[109] <- "experience3" 
df6 <- names(df6a)[110] <- "experience4" 
df6 <- names(df6a)[111] <- "experience5" 
df6 <- names(df6a)[112] <- "experience6" 
df6 <- names(df6a)[113] <- "experience7" 
df6 <- names(df6a)[114] <- "experience8" 
df6 <- names(df6a)[115] <- "experience9" 

###AV Rename all duplicates of "If you’re unlikely to pursue an academic research 
#career, what are the main reasons??" and make unique
df6 <- names(df6a)[130] <- "reasonUnlikelyAcademicCarreerPursuit1" 
df6 <- names(df6a)[131] <- "reasonUnlikelyAcademicCarreerPursuit2" 
df6 <- names(df6a)[132] <- "reasonUnlikelyAcademicCarreerPursuit3" 
df6 <- names(df6a)[133] <- "reasonUnlikelyAcademicCarreerPursuit4" 
df6 <- names(df6a)[134] <- "reasonUnlikelyAcademicCarreerPursuit5" 
df6 <- names(df6a)[135] <- "reasonUnlikelyAcademicCarreerPursuit6" 
df6 <- names(df6a)[136] <- "reasonUnlikelyAcademicCarreerPursuit7" 
df6 <- names(df6a)[137] <- "reasonUnlikelyAcademicCarreerPursuit8" 
df6 <- names(df6a)[138] <- "reasonUnlikelyAcademicCarreerPursuit9" 

###AV Rename all duplicates of "How did you arrive at your current career decision? 
#Plea..." and make unique
df6 <- names(df6a)[147] <- "HowArriveAtCareerDecision1" 
df6 <- names(df6a)[148] <- "HowArriveAtCareerDecision2" 
df6 <- names(df6a)[149] <- "HowArriveAtCareerDecision3" 
df6 <- names(df6a)[151] <- "HowArriveAtCareerDecision4" 
df6 <- names(df6a)[152] <- "HowArriveAtCareerDecision5" 
df6 <- names(df6a)[153] <- "HowArriveAtCareerDecision6" 
df6 <- names(df6a)[154] <- "HowArriveAtCareerDecision7" 
df6 <- names(df6a)[155] <- "HowArriveAtCareerDecision8" 
df6 <- names(df6a)[156] <- "HowArriveAtCareerDecision9" 
df6 <- names(df6a)[157] <- "HowArriveAtCareerDecision10" 

###AV Rename all duplicates of "How do you learn about available career 
#opportunities that are beyond academia?" and make unique
df6 <- names(df6a)[159] <- "HowLearnCareerNotAcademia1" 
df6 <- names(df6a)[160] <- "HowLearnCareerNotAcademia2" 
df6 <- names(df6a)[161] <- "HowLearnCareerNotAcademia3" 
df6 <- names(df6a)[162] <- "HowLearnCareerNotAcademia4" 
df6 <- names(df6a)[163] <- "HowLearnCareerNotAcademia5" 
df6 <- names(df6a)[164] <- "HowLearnCareerNotAcademia6" 
df6 <- names(df6a)[165] <- "HowLearnCareerNotAcademia7" 
df6 <- names(df6a)[166] <- "HowLearnCareerNotAcademia8" 
df6 <- names(df6a)[167] <- "HowLearnCareerNotAcademia9" 
df6 <- names(df6a)[168] <- "HowLearnCareerNotAcademia10" 
df6 <- names(df6a)[169] <- "HowLearnCareerNotAcademia11" 
df6 <- names(df6a)[170] <- "HowLearnCareerNotAcademia12" 
df6 <- names(df6a)[171] <- "HowLearnCareerNotAcademia13" 
df6 <- names(df6a)[172] <- "HowLearnCareerNotAcademia14" 

###AV Rename all duplicates of "Which of the following 3 things would you say are 
#the most difficult for PhD students in your discipline?" and make unique
df6 <- names(df6a)[174] <- "DifficultInDiscipline1" 
df6 <- names(df6a)[175] <- "DifficultInDiscipline2" 
df6 <- names(df6a)[176] <- "DifficultInDiscipline3" 
df6 <- names(df6a)[177] <- "DifficultInDiscipline4" 
df6 <- names(df6a)[178] <- "DifficultInDiscipline5" 
df6 <- names(df6a)[179] <- "DifficultInDiscipline6" 
df6 <- names(df6a)[180] <- "DifficultInDiscipline7" 
df6 <- names(df6a)[181] <- "DifficultInDiscipline8" 
df6 <- names(df6a)[182] <- "DifficultInDiscipline9" 

###AV Rename all duplicates of "Which of the following would you say are the 
#most difficult for PhD students in the country where you are studying?" and make unique
df6 <- names(df6a)[184] <- "DifficultInCountry1" 
df6 <- names(df6a)[185] <- "DifficultInCountry2" 
df6 <- names(df6a)[186] <- "DifficultInCountry3" 
df6 <- names(df6a)[187] <- "DifficultInCountry4" 
df6 <- names(df6a)[188] <- "DifficultInCountry5" 
df6 <- names(df6a)[189] <- "DifficultInCountry6" 
df6 <- names(df6a)[190] <- "DifficultInCountry7" 

###AV Rename all duplicates of "Which of the following resources do you think PhD 
#students need the most in order to establish a satisfying career?" and make unique
df6 <- names(df6a)[192] <- "ResourcesForSatisfyingCareer1" 
df6 <- names(df6a)[193] <- "ResourcesForSatisfyingCareer2" 
df6 <- names(df6a)[194] <- "ResourcesForSatisfyingCareer3" 
df6 <- names(df6a)[195] <- "ResourcesForSatisfyingCareer4" 
df6 <- names(df6a)[196] <- "ResourcesForSatisfyingCareer5" 
df6 <- names(df6a)[197] <- "ResourcesForSatisfyingCareer6" 
df6 <- names(df6a)[198] <- "ResourcesForSatisfyingCareer7" 
df6 <- names(df6a)[199] <- "ResourcesForSatisfyingCareer8" 

###AV Rename all duplicates of "Which, if any, of the following activities have 
#you done to advance your career?" and make unique
df6 <- names(df6a)[217] <- "ActivitiesToAdvanceCareer1" 
df6 <- names(df6a)[218] <- "ActivitiesToAdvanceCareer2" 
df6 <- names(df6a)[219] <- "ActivitiesToAdvanceCareer3" 
df6 <- names(df6a)[220] <- "ActivitiesToAdvanceCareer4" 
df6 <- names(df6a)[221] <- "ActivitiesToAdvanceCareer5" 
df6 <- names(df6a)[222] <- "ActivitiesToAdvanceCareer6" 
df6 <- names(df6a)[223] <- "ActivitiesToAdvanceCareer7" 
df6 <- names(df6a)[224] <- "ActivitiesToAdvanceCareer8" 

###AV Rename all duplicates of "Which of the following social media networks have 
#you used to build your professional network" and make unique
df6 <- names(df6a)[226] <- "SocialMediaToBuildNetwork1" 
df6 <- names(df6a)[227] <- "SocialMediaToBuildNetwork2" 
df6 <- names(df6a)[228] <- "SocialMediaToBuildNetwork3" 
df6 <- names(df6a)[229] <- "SocialMediaToBuildNetwork4" 
df6 <- names(df6a)[230] <- "SocialMediaToBuildNetwork5" 
df6 <- names(df6a)[231] <- "SocialMediaToBuildNetwork6" 
df6 <- names(df6a)[232] <- "SocialMediaToBuildNetwork7" 

###AV Rename all duplicates of "What would you do differently right now if you 
#were starting your programme?" and make unique
df6 <- names(df6a)[234] <- "DoDifferently1" 
df6 <- names(df6a)[235] <- "DoDifferently2" 
df6 <- names(df6a)[236] <- "DoDifferently3" 
df6 <- names(df6a)[237] <- "DoDifferently4" 
df6 <- names(df6a)[238] <- "DoDifferently5" 

###AV Rename all duplicates of "Which of the following best describes you?" 
#and make unique
df6 <- names(df6a)[243] <- "BestDescribes1" 
df6 <- names(df6a)[244] <- "BestDescribes2" 
df6 <- names(df6a)[245] <- "BestDescribes3" 
df6 <- names(df6a)[246] <- "BestDescribes4" 
df6 <- names(df6a)[247] <- "BestDescribes5" 
df6 <- names(df6a)[248] <- "BestDescribes6" 
df6 <- names(df6a)[249] <- "BestDescribes7" 
df6 <- names(df6a)[250] <- "BestDescribes8" 
df6 <- names(df6a)[251] <- "BestDescribes9" 
df6 <- names(df6a)[252] <- "BestDescribes10"
df6 <- names(df6a)[253] <- "BestDescribes11" 
df6 <- names(df6a)[254] <- "BestDescribes12"

###AV Rename all duplicates of "Do you have any caring responsibilities" and 
#make unique
df6 <- names(df6a)[256] <- "CaringResponsibilities1" 
df6 <- names(df6a)[257] <- "CaringResponsibilities2" 
df6 <- names(df6a)[258] <- "CaringResponsibilities3" 
df6 <- names(df6a)[259] <- "CaringResponsibilities4" 
df6 <- names(df6a)[260] <- "CaringResponsibilities5" 


###AV Final Important Bits, one more rename and the declaration that makes 
#renaming work.
df6 <- names(df6a)[242] <- "Gender" 
df6 <- names(df6a)[13]  <- "Immigrant" 
df6 <- df6a


###AV Workflow Notes:
###AV This bit told me what ought to be renamed and made not identical
###rename(df6, combine1 = 150)

###AV This is the template I used to fill in the above lines, without 
#the "#" infront of each line.

####AV Rename all duplicates of "" and make unique
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 


###Finished Product: df7
df7 <- df6

```

Here I separate and then combine demographic data, collapsing the multiple columns that the data is stored in into a single new column, while keeping the original columns, and converting NA values back to NA values from character values "NA", as the unite feature seems to turn NA into "NA" as an indirect consequence of its usage.
```{r}
df8  <- unite(df7, "ethnicityGroupedOther",  243:254, remove = FALSE, na.rm = TRUE)
#df7 %>% unite("ethnicityOtherWriteInIncluded", 2,remove= FALSE) specified22 is variable 
#that has the write-in ethnicity data
df9  <- unite(df8, "ethnicityOtherWriteInNotYetIncluded", 244:252, remove = FALSE, na.rm = TRUE)
###AV Ensure that all NA values remain as NA, as the above unite processes seem 
#to convert NA to blanks after uniting. Comment out the 2 lines below to confirm.
df10 <- df9 
df10[df10 == ""] <- NA 
###AV finally combine them all
df11 <- unite(df10, "ethnicityOtherWriteInIncluded", 
              c('ethnicityOtherWriteInNotYetIncluded', 
                'specified22') , remove = FALSE, na.rm = TRUE)
```

<br>

<br>

<br>


--------- Everything Below This Line Probably Requires df12 or Some Variation of df11 ---------

<br>

I must note that the cleaning of the demographic data will not be used in this analysis, as I am focusing on gender and immigration, and not on ethnicity. I will analyze ethnicity and clean the whole of the dataset at another time, however time has limited my capacity to do everything I want to do here. But this is EDA, so the clear and distinct lack of direction is a feature, not a bug.

<br>


## Immigration Analysis against Training and Readiness (Q50) Responses and Other Selections

### Data Selection, Renaming, And Compillation

Immigration count and Immigrant proportion analysis
```{r}
###Output A Table and dataframe with the values needed
tableImmigrant <- table(df11['Immigrant'])
ImmigrantCount<- as.data.frame(tableImmigrant)

###Proportional Analysis
ImmigrantProportion <- as.data.frame(table(df11$Immigrant)/length(df11$Immigrant))
###Display Output genderProportion, note that the question asks are you not an immigrant,
#so an immigrant would have answered "No" and a non-immigrant would answer "Yes"

ImmigrantProportion

```


Creation of different data frames for analysis by Immigrant, against training efficacy for certain tasks(Q50),
which will be used in a later analysis.
```{r}
df12Imm <- df11[c(13,55,56,77,78,87,96,106,
                  201,202,203,204,205,206,207,208,209,210,211,212,213,214,215,216,
                  242)]

df12ImmNo <- df12Imm[df12Imm$'Immigrant' == 'Yes',]
df12ImmYes <- df12Imm[df12Imm$'Immigrant' == 'No',]

```

Creation of ancillary and working data frames.
```{r}

df13Imm <- df12Imm
df14Imm <- df13Imm
df14Imm <- df13Imm

```


Some data transformations and a rename, so that I could copy and paste from online sources which predominantly use "df" or "data" and not df23 or whatever I'm doing. Here is where I seem to have renamed df12's Collecting column and not df12m's, accounting for the difference between the two.

<br>

<br>

Rename All Columns With Meaningful Names.
```{r}

df15Imm <- names(df12Imm)[1]   <- "Immigration"

df15Imm <- names(df12Imm)[2]   <- "SatisfiedWithDecisionPhD"
df15Imm <- names(df12Imm)[3]   <- "SatisfiedWithPhDExperience"
df15Imm <- names(df12Imm)[4]   <- "HoursAWeekPhDProgram"
df15Imm <- names(df12Imm)[5]   <- "HoursWithSupervisor"
df15Imm <- names(df12Imm)[6]   <- "AnxietyOrDepression"
df15Imm <- names(df12Imm)[7]   <- "Bullying"
df15Imm <- names(df12Imm)[8]   <- "DiscriminationOrHarassment"

df15Imm <- names(df12Imm)[9]   <- "Collecting"
df15Imm <- names(df12Imm)[10]  <- "Analyzing"
df15Imm <- names(df12Imm)[11]  <- "Designing"
df15Imm <- names(df12Imm)[12]  <- "Writing"
df15Imm <- names(df12Imm)[13]  <- "DevResistance"
df15Imm <- names(df12Imm)[14]  <- "PresentingSpecialist"
df15Imm <- names(df12Imm)[15]  <- "PresentingPublic"
df15Imm <- names(df12Imm)[16]  <- "ApplyingFunding"
df15Imm <- names(df12Imm)[17]  <- "SatisCareer"
df15Imm <- names(df12Imm)[18]  <- "MngCompProj"
df15Imm <- names(df12Imm)[19]  <- "DevBusinessPlan"
df15Imm <- names(df12Imm)[20]  <- "MngPeople"
df15Imm <- names(df12Imm)[21]  <- "MngLargeBudget"
df15Imm <- names(df12Imm)[22]  <- "FeelProgPrepResearch"
df15Imm <- names(df12Imm)[23]  <- "FeelProgPrepScience"
df15Imm <- names(df12Imm)[24]  <- "FeelProgPrepMixIndAcad"

df15Imm <- names(df12Imm)[25]  <- "Gender"



df15Imm <- df12Imm
dfImm <- df15Imm
```

Analysis for "Collecting data" variable as a proportion of its answers
```{r}
TableCollectingProportion <- table(df12Imm$Collecting)/length(df12Imm$Collecting)


DFCollectingProportion <- as.data.frame(TableCollectingProportion)

DFCollectingProportion
```


<br>

### Graphs for Immigration

<br>

<br>

#### Immigration Against Collecting

<br>

Column: Collecting
Data frame: graphdf1Immigration 
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1Immigration <- dfImm

###Keep all values that are not containing "Unsure/Not applicable"
graphdf1Immigration <- graphdf1Immigration[!(graphdf1Immigration$Collecting == "Unsure/Not applicable"),]

###Refresh old graphdf1Immigration with data_new1 info
graphdf1Immigration <- graphdf1Immigration

###Set variable order
graphdf1Immigration$Collecting <- factor(graphdf1Immigration$Collecting , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = dfImm) + 
  geom_bar(mapping = aes(x = Immigration, fill = Collecting), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against Analyzing Data

<br>

Column: Analyzing
Data frame: graphdfImmigrationAnalyzing
```{r}
graphdfImmigrationAnalyzing <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationAnalyzing<- graphdfImmigrationAnalyzing[!(graphdfImmigrationAnalyzing$Analyzing == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationAnalyzing <- graphdfImmigrationAnalyzing
#Set variable order
graphdfImmigrationAnalyzing$Analyzing <- factor(graphdfImmigrationAnalyzing$Analyzing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationAnalyzing) + 
  geom_bar(mapping = aes(x = Immigration, fill = Analyzing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Designing robust reproducible experiments

<br>

Column: Designing
Data frame: graphdfImmigrationDesigning
```{r}
graphdfImmigrationDesigning <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationDesigning<- graphdfImmigrationDesigning[!(graphdfImmigrationDesigning$Designing == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationDesigning <- graphdfImmigrationDesigning
#Set variable order
graphdfImmigrationDesigning$Designing <- factor(graphdfImmigrationDesigning$Designing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationDesigning) + 
  geom_bar(mapping = aes(x = Immigration, fill = Designing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Writing a paper for publication in a peer-reviewed journal

<br>

Column: Writing
graphdfImmigrationWriting
```{r}
graphdfImmigrationWriting <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationWriting<- graphdfImmigrationWriting[!(graphdfImmigrationWriting$Writing == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationWriting <- graphdfImmigrationWriting
#Set variable order
graphdfImmigrationWriting$Writing <- factor(graphdfImmigrationWriting$Writing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationWriting) + 
  geom_bar(mapping = aes(x = Immigration, fill = Writing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Developing resilience to manage rejection by a peer review panel

<br>

Column: DevResistance
Data frame: graphdfImmigrationDevResistance
```{r}
graphdfImmigrationDevResistance <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationDevResistance<- graphdfImmigrationDevResistance[!(graphdfImmigrationDevResistance$DevResistance == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationDevResistance <- graphdfImmigrationDevResistance
#Set variable order
graphdfImmigrationDevResistance$DevResistance <- factor(graphdfImmigrationDevResistance$DevResistance , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationDevResistance) + 
  geom_bar(mapping = aes(x = Immigration, fill = DevResistance), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Presenting findings to a specialist audience

<br>

Column: PresentingSpecialist
Data frame: graphdfImmigrationPresentingSpecialist
```{r}
graphdfImmigrationPresentingSpecialist <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationPresentingSpecialist<- graphdfImmigrationPresentingSpecialist[!(graphdfImmigrationPresentingSpecialist$PresentingSpecialist == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationPresentingSpecialist <- graphdfImmigrationPresentingSpecialist
#Set variable order
graphdfImmigrationPresentingSpecialist$PresentingSpecialist <- factor(graphdfImmigrationPresentingSpecialist$PresentingSpecialist , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationPresentingSpecialist) + 
  geom_bar(mapping = aes(x = Immigration, fill = PresentingSpecialist), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Presenting findings to a non-specialist (public) audience

<br>

Column: PresentingPublic
Data frame: graphdfImmigrationPresentingPublic
```{r}
graphdfImmigrationPresentingPublic <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationPresentingPublic<- graphdfImmigrationPresentingPublic[!(graphdfImmigrationPresentingPublic$PresentingPublic == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationPresentingPublic <- graphdfImmigrationPresentingPublic
#Set variable order
graphdfImmigrationPresentingPublic$PresentingPublic <- factor(graphdfImmigrationPresentingPublic$PresentingPublic , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationPresentingPublic) + 
  geom_bar(mapping = aes(x = Immigration, fill = PresentingPublic), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Finding a Applying for funding

<br>

Column: ApplyingFunding
Data frame: graphdfImmigrationApplyingFunding
```{r}
graphdfImmigrationApplyingFunding <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationApplyingFunding<- graphdfImmigrationApplyingFunding[!(graphdfImmigrationApplyingFunding$ApplyingFunding == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationApplyingFunding <- graphdfImmigrationApplyingFunding
#Set variable order
graphdfImmigrationApplyingFunding$ApplyingFunding <- factor(graphdfImmigrationApplyingFunding$ApplyingFunding , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationApplyingFunding) + 
  geom_bar(mapping = aes(x = Immigration, fill = ApplyingFunding), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Finding a satisfying career

<br>

Column: SatisCareer
Data frame: graphdfImmigrationSatisCareer
```{r}
graphdfImmigrationSatisCareer <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationSatisCareer<- graphdfImmigrationSatisCareer[!(graphdfImmigrationSatisCareer$SatisCareer == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationSatisCareer <- graphdfImmigrationSatisCareer
#Set variable order
graphdfImmigrationSatisCareer$SatisCareer <- factor(graphdfImmigrationSatisCareer$SatisCareer , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationSatisCareer) + 
  geom_bar(mapping = aes(x = Immigration, fill = SatisCareer), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Managing complex projects

<br>

Column: MngCompProj
Data frame: graphdfImmigrationMngCompProj
```{r}
graphdfImmigrationMngCompProj <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationMngCompProj<- graphdfImmigrationMngCompProj[!(graphdfImmigrationMngCompProj$MngCompProj == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationMngCompProj <- graphdfImmigrationMngCompProj
#Set variable order
graphdfImmigrationMngCompProj$MngCompProj <- factor(graphdfImmigrationMngCompProj$MngCompProj , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationMngCompProj) + 
  geom_bar(mapping = aes(x = Immigration, fill = MngCompProj), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Developing a business plan

<br>

Column: DevBusinessPlan
Data frame: graphdfImmigrationDevBusinessPlan
```{r}
graphdfImmigrationDevBusinessPlan <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationDevBusinessPlan<- graphdfImmigrationDevBusinessPlan[!(graphdfImmigrationDevBusinessPlan$DevBusinessPlan == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationDevBusinessPlan <- graphdfImmigrationDevBusinessPlan
#Set variable order
graphdfImmigrationDevBusinessPlan$DevBusinessPlan <- factor(graphdfImmigrationDevBusinessPlan$DevBusinessPlan , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationDevBusinessPlan) + 
  geom_bar(mapping = aes(x = Immigration, fill = DevBusinessPlan), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Managing people

<br>

Column: MngPeople
Data frame: graphdfImmigrationMngPeople
```{r}
graphdfImmigrationMngPeople <- dfImm
#Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationMngPeople<- graphdfImmigrationMngPeople[!(graphdfImmigrationMngPeople$MngPeople == "Unsure/Not applicable"),]
# update data frame
graphdfImmigrationMngPeople <- graphdfImmigrationMngPeople
#Set variable order
graphdfImmigrationMngPeople$MngPeople <- factor(graphdfImmigrationMngPeople$MngPeople , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

#Plot
ggplot(data = graphdfImmigrationMngPeople) + 
  geom_bar(mapping = aes(x = Immigration, fill = MngPeople), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against Managing a large operational budget

<br>

Column: MngLargeBudget
Data frame: graphdfImmigrationMngLargeBudget
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationMngLargeBudget <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationMngLargeBudget<- graphdfImmigrationMngLargeBudget[!(graphdfImmigrationMngLargeBudget$MngLargeBudget == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdfImmigrationMngLargeBudget <- graphdfImmigrationMngLargeBudget

###Set variable order
graphdfImmigrationMngLargeBudget$MngLargeBudget <- factor(graphdfImmigrationMngLargeBudget$MngLargeBudget , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdfImmigrationMngLargeBudget) + 
  geom_bar(mapping = aes(x = Immigration, fill = MngLargeBudget), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against I feel that my programme is preparing me well for a research career

<br>

Column: FeelProgPrepResearch
Data frame: graphdfImmigrationFeelProgPrepResearch
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationFeelProgPrepResearch <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationFeelProgPrepResearch<- graphdfImmigrationFeelProgPrepResearch[!(graphdfImmigrationFeelProgPrepResearch$FeelProgPrepResearch == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdfImmigrationFeelProgPrepResearch <- graphdfImmigrationFeelProgPrepResearch

###Set variable order
graphdfImmigrationFeelProgPrepResearch$FeelProgPrepResearch <- factor(graphdfImmigrationFeelProgPrepResearch$FeelProgPrepResearch , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdfImmigrationFeelProgPrepResearch) + 
  geom_bar(mapping = aes(x = Immigration, fill = FeelProgPrepResearch), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against I feel that my programme is perparing me well for a non-research science-related career

<br>

Column: FeelProgPrepScience
Data frame: graphdfImmigrationFeelProgPrepScience
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationFeelProgPrepScience <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationFeelProgPrepScience<- graphdfImmigrationFeelProgPrepScience[!(graphdfImmigrationFeelProgPrepScience$FeelProgPrepScience == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdfImmigrationFeelProgPrepScience <- graphdfImmigrationFeelProgPrepScience

###Set variable order
graphdfImmigrationFeelProgPrepScience$FeelProgPrepScience <- factor(graphdfImmigrationFeelProgPrepScience$FeelProgPrepScience , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdfImmigrationFeelProgPrepScience) + 
  geom_bar(mapping = aes(x = Immigration, fill = FeelProgPrepScience), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Immigration Against I feel that my programme is preparing me well for a career that straddles both industry and academia

<br>

Column: FeelProgPrepMixIndAcad
Data frame: graphdfImmigrationFeelProgPrepMixIndAcad
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationFeelProgPrepMixIndAcad <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationFeelProgPrepMixIndAcad<- graphdfImmigrationFeelProgPrepMixIndAcad[!(graphdfImmigrationFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdfImmigrationFeelProgPrepMixIndAcad <- graphdfImmigrationFeelProgPrepMixIndAcad

###Set variable order
graphdfImmigrationFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad <- factor(graphdfImmigrationFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdfImmigrationFeelProgPrepMixIndAcad) + 
  geom_bar(mapping = aes(x = Immigration, fill = FeelProgPrepMixIndAcad), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against I am satisfied with my decision to pursue a PhD

<br>

Column: SatisfiedWithDecisionPhD
Data frame: graphdfImmigrationSatisfiedWithDecisionPhD
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationSatisfiedWithDecisionPhD <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
#graphdfImmigrationSatisfiedWithPhDExperience<- graphdfImmigrationSatisfiedWithPhDExperience[!(graphdfImmigrationSatisfiedWithPhDExperience$SatisfiedWithPhDExperience == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
#graphdfImmigrationSatisfiedWithPhDExperience <- graphdfImmigrationSatisfiedWithPhDExperience
#
###Set variable order
graphdfImmigrationSatisfiedWithDecisionPhD$SatisfiedWithDecisionPhD <- factor(graphdfImmigrationSatisfiedWithDecisionPhD$SatisfiedWithDecisionPhD , levels=c("Very dissatisfied", "Somewhat dissatisfied", "Neither satisfied nor dissatisfied", "Somewhat satisfied", "Very satisfied"))

##Plot
ggplot(data = graphdfImmigrationSatisfiedWithDecisionPhD) + 
  geom_bar(mapping = aes(x = Immigration, fill = SatisfiedWithDecisionPhD), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against I am satisfied with my experience

<br>

Column: SatisfiedWithPhDExperience
Data frame: graphdfImmigrationSatisfiedWithPhDExperience
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationSatisfiedWithPhDExperience <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
#graphdfImmigrationSatisfiedWithPhDExperience<- graphdfImmigrationSatisfiedWithPhDExperience[!(graphdfImmigrationSatisfiedWithPhDExperience$SatisfiedWithDecisionPhD == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdfImmigrationSatisfiedWithPhDExperience <- graphdfImmigrationSatisfiedWithPhDExperience

###Set variable order
graphdfImmigrationSatisfiedWithPhDExperience$SatisfiedWithPhDExperience <- factor(graphdfImmigrationSatisfiedWithPhDExperience$SatisfiedWithPhDExperience , levels=c("1 = Not at all satisfied", "2", "3", "4 = Neither satisfied nor dissatisfied", "5","6", "7 = Extremely satisfied"))

##Plot
ggplot(data = graphdfImmigrationSatisfiedWithPhDExperience) + 
  geom_bar(mapping = aes(x = Immigration, fill = SatisfiedWithPhDExperience), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against Hours a week on my program

<br>

Column: HoursAWeekPhDProgram
Data frame: graphdfImmigrationHoursAWeekPhDProgram
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationHoursAWeekPhDProgram <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
#graphdfImmigrationHoursAWeekPhDProgram<- graphdfImmigrationHoursAWeekPhDProgram[!(graphdfImmigrationHoursAWeekPhDProgram$HoursAWeekPhDProgram == "Other, please specify"),]

###Refresh old graphdf1gender with data_new1 info
#graphdfImmigrationHoursAWeekPhDProgram <- graphdfImmigrationHoursAWeekPhDProgram

###Set variable order
graphdfImmigrationHoursAWeekPhDProgram$HoursAWeekPhDProgram <- factor(graphdfImmigrationHoursAWeekPhDProgram$HoursAWeekPhDProgram , levels=c("Less than 11 hours","11-20 hours", "21-30 hours","31-40 hours","41-50 hours","51-60 hours","61-70 hours","71-80 hours","More than 80 hours"))

##Plot
ggplot(data = graphdfImmigrationHoursAWeekPhDProgram) + 
  geom_bar(mapping = aes(x = Immigration, fill = HoursAWeekPhDProgram), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against Hours a week with my advisor

<br>

Column: HoursWithSupervisor
Data frame: graphdfImmigrationHoursWithSupervisor
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationHoursWithSupervisor <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
graphdfImmigrationHoursWithSupervisor <- graphdfImmigrationHoursWithSupervisor[!(graphdfImmigrationHoursWithSupervisor$HoursWithSupervisor == "Other, please specify"),]

###Refresh old graphdf1gender with data_new1 info
#graphdfImmigrationHoursWithSupervisor <- graphdfImmigrationHoursWithSupervisor

###Set variable order
graphdfImmigrationHoursWithSupervisor$HoursWithSupervisor <- factor(graphdfImmigrationHoursWithSupervisor$HoursWithSupervisor , levels=c("Less than an hour","Between one and three hours", "More than three hours"))

##Plot
ggplot(data = graphdfImmigrationHoursWithSupervisor) + 
  geom_bar(mapping = aes(x = Immigration, fill = HoursWithSupervisor), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against I have seeked help for phd anxiety or deppression

<br>

Column: AnxietyOrDepression
Data frame: graphdfImmigrationAnxietyOrDepression 
Note: (Kept NA values since they could be interpreted as apathy or negativity, however inclusion doesnt seem to add mcuh to the overall image)
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationAnxietyOrDepression <- dfImm

###Set variable order
graphdfImmigrationAnxietyOrDepression$AnxietyOrDepression <- factor(graphdfImmigrationAnxietyOrDepression$AnxietyOrDepression , levels=c("Yes", "No", "Prefer not to say"))

##Plot
ggplot(data = graphdfImmigrationAnxietyOrDepression) + 
  geom_bar(mapping = aes(x = Immigration, fill = AnxietyOrDepression), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

<br>

#### Immigration Against Bullying Experienced

Column: Bullying
Data frame: graphdfImmigrationBullying
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationBullying <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
#graphdfImmigrationFeelProgPrepMixIndAcad<- graphdfImmigrationFeelProgPrepMixIndAcad[!(graphdfImmigrationFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
#graphdfImmigrationFeelProgPrepMixIndAcad <- graphdfImmigrationFeelProgPrepMixIndAcad

###Set variable order
graphdfImmigrationBullying$Bullying <- factor(graphdfImmigrationBullying$Bullying , levels=c("Yes", "Prefer not to say","No"))

##Plot
ggplot(data = graphdfImmigrationBullying) + 
  geom_bar(mapping = aes(x = Immigration, fill = Bullying), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against Experienced discrimination or harassment

<br>

Column: DiscriminationOrHarassment
Data frame: graphdfImmigrationDiscriminationOrHarassment
```{r}
###New data frame, to ensure there are no issues down the line
graphdfImmigrationDiscriminationOrHarassment <- dfImm
###Keep all values that are not containing "Unsure/Not applicable"
#graphdfImmigrationDiscriminationOrHarassment<- graphdfImmigrationDiscriminationOrHarassment[!(graphdfImmigrationDiscriminationOrHarassment$DiscriminationOrHarassment == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
#graphdfImmigrationDiscriminationOrHarassment <- graphdfImmigrationDiscriminationOrHarassment

###Set variable order
graphdfImmigrationDiscriminationOrHarassment$DiscriminationOrHarassment <- factor(graphdfImmigrationDiscriminationOrHarassment$DiscriminationOrHarassment, levels=c("Yes", "Prefer not to say", "No"))
##Plot
ggplot(data = graphdfImmigrationDiscriminationOrHarassment) + 
  geom_bar(mapping = aes(x = Immigration, fill = DiscriminationOrHarassment), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


#### Immigration Against Gender

<br>

Column: Gender
Data frame: graphdfGenderAndImmigration
```{r}
###New data frame, to ensure there are no issues down the line
graphdfGenderAndImmigration <- dfImm

##Plot
ggplot(data = graphdfGenderAndImmigration) + 
  geom_bar(mapping = aes(x = Immigration, fill = Gender), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```










## Gender Analysis against Training and Readiness (Q50) Responses and Other Selections

### Data Selection, Renaming, And Compillation

<br>


<br>

Gender count and gender proportion analysis, and data frame creation
```{r}
###Output A Table and dataframe with the values needed
tableGender <- table(df11['Gender'])
genderCount<- as.data.frame(tableGender)

###Proportional Analysis
genderProportion <- as.data.frame(table(df11$Gender)/length(df11$Gender))
###Display Output genderProportion
genderProportion
```

Creation of different data frames for analysis by gender, against training efficacy for certain tasks(Q50). Not used here but will be used later on.
```{r}
df12 <- df11[c(201,202,203,204,205,206,207,208,209,210,211,212,213,214,215,216,242)]

df12M <- df12[df12$'Gender' == 'Male (including trans male)',]
df12F <- df12[df12$'Gender' == 'Female (including trans female)',]
df12GQNB <- df12[df12$'Gender' == 'Gender queer / Non binary',]
```

A workflow for analysis of gender by creating seperate dataframes, using data frame with only "Male (including trans male)" as an example.
```{r}

###Select relevant columns/variables

### Rename Variable/Column to be analyzed, the dependent, by index
df13M <- df12M
df14M <- df13M
df14M <- names(df13M)[1] <- "Collecting"
df14M <- df13M


###Plot the bit
#ggplot(df14M, aes( Collecting, colour = Gender)) +   geom_bar() ###Just another way to plot the data

barplotMCollectingData <- ggplot(df14M, aes( Collecting, colour = Gender)) + 
  geom_bar()+
  scale_x_discrete(guide = guide_axis(n.dodge=2))

###Display Plot
barplotMCollectingData

```



New data frame for gender and transformation of previous dataframe into one that will plug in directly. I wrote the code for gender first, but dfImm allows for a larger number of analysies, so I will just copy it in, and it still ought to work.
```{r}
dfGen <- dfImm
 
df15 <- dfGen
df <- df15
```



### Graphs for Gender

<br>

<br>

####Gender against Collecting Data 

<br>

first graph for gender against collecting data, not incredibly interesting, and also hampered by small sample size of Gender Queer/Non Binary and Prefer Not To Say
```{r}

groupedBarGenderCollecting <- ggplot(data = df) + 
  geom_bar(mapping = aes(x = Gender, fill = Collecting), position = "dodge")+
  scale_colour_brewer(palette = "BrBG") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))


groupedBarGenderCollecting

```

<br>

A better proportional graph. This chunk also contains the code to reorder variables manually.
```{r}
data_new <- df
df <- data_new

df$Collecting <- factor(df$Collecting , 
                        levels=c("Very badly", "Badly", "Neither well nor badly", 
                                 "Well", "Very well", "Unsure/Not applicable"))

data_new <- df
df <- data_new

ggplot(data = data_new) + 
  geom_bar(mapping = aes(x = Gender, fill = Collecting), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))

```
Not bad, however the not sure/not applicable bit is distorting our visual analysis.


<br>


Same proportional graph, without the "Unsure/Not applicable" value
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1gender <- df
###Keep all values that are not containing "Unsure/Not applicable"
data_new1 <- graphdf1gender[!(graphdf1gender$Collecting == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1gender <- data_new1

###Set variable order
graphdf1gender$Collecting <- factor(graphdf1gender$Collecting , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = data_new1) + 
  geom_bar(mapping = aes(x = Gender, fill = Collecting), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```


<br>

#### Gender Against Analyzing Data

<br>

Column: Analyzing
Data Frame: graphdf1genderAnalyzing
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderAnalyzing <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderAnalyzing<- graphdf1genderAnalyzing[!(graphdf1genderAnalyzing$Analyzing == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderAnalyzing <- graphdf1genderAnalyzing

###Set variable order
graphdf1genderAnalyzing$Analyzing <- factor(graphdf1genderAnalyzing$Analyzing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderAnalyzing) + 
  geom_bar(mapping = aes(x = Gender, fill = Analyzing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Designing robust reproducible experiments

<br>

Column: Designing
Data Frame: graphdf1genderDesigning
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderDesigning <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderDesigning<- graphdf1genderDesigning[!(graphdf1genderDesigning$Designing == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderDesigning <- graphdf1genderDesigning

###Set variable order
graphdf1genderDesigning$Designing <- factor(graphdf1genderDesigning$Designing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderDesigning) + 
  geom_bar(mapping = aes(x = Gender, fill = Designing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Writing a paper for publication in a peer-reviewed journal

<br>

Column: Writing
Data Frame: graphdf1genderWriting
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderWriting <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderWriting<- graphdf1genderWriting[!(graphdf1genderWriting$Writing == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderWriting <- graphdf1genderWriting

###Set variable order
graphdf1genderWriting$Writing <- factor(graphdf1genderWriting$Writing , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderWriting) + 
  geom_bar(mapping = aes(x = Gender, fill = Writing), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Developing resilience to manage rejection by a peer review panel

<br>

Column: DevResistance
Data Frame: graphdf1genderDevResistance
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderDevResistance <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderDevResistance<- graphdf1genderDevResistance[!(graphdf1genderDevResistance$DevResistance == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderDevResistance <- graphdf1genderDevResistance

###Set variable order
graphdf1genderDevResistance$DevResistance <- factor(graphdf1genderDevResistance$DevResistance , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderDevResistance) + 
  geom_bar(mapping = aes(x = Gender, fill = DevResistance), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Presenting findings to a specialist audience

<br>

Column: PresentingSpecialist
Data Frame: graphdf1genderPresentingSpecialist
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderPresentingSpecialist <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderPresentingSpecialist<- graphdf1genderPresentingSpecialist[!(graphdf1genderPresentingSpecialist$PresentingSpecialist == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderPresentingSpecialist <- graphdf1genderPresentingSpecialist

###Set variable order
graphdf1genderPresentingSpecialist$PresentingSpecialist <- factor(graphdf1genderPresentingSpecialist$PresentingSpecialist , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderPresentingSpecialist) + 
  geom_bar(mapping = aes(x = Gender, fill = PresentingSpecialist), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Presenting findings to a non-specialist (public) audience

<br>

Column: PresentingPublic
Data Frame: graphdf1genderPresentingPublic
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderPresentingPublic <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderPresentingPublic<- graphdf1genderPresentingPublic[!(graphdf1genderPresentingPublic$PresentingPublic == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderPresentingPublic <- graphdf1genderPresentingPublic

###Set variable order
graphdf1genderPresentingPublic$PresentingPublic <- factor(graphdf1genderPresentingPublic$PresentingPublic , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderPresentingPublic) + 
  geom_bar(mapping = aes(x = Gender, fill = PresentingPublic), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Finding a Applying for funding

<br>

Column: ApplyingFunding
Data Frame: graphdf1genderApplyingFunding
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderApplyingFunding <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderApplyingFunding<- graphdf1genderApplyingFunding[!(graphdf1genderApplyingFunding$ApplyingFunding == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderApplyingFunding <- graphdf1genderApplyingFunding

###Set variable order
graphdf1genderApplyingFunding$ApplyingFunding <- factor(graphdf1genderApplyingFunding$ApplyingFunding , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderApplyingFunding) + 
  geom_bar(mapping = aes(x = Gender, fill = ApplyingFunding), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Finding a satisfying career

<br>

Column: SatisCareer
Data Frame: graphdf1genderSatisCareer
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderSatisCareer <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderSatisCareer<- graphdf1genderSatisCareer[!(graphdf1genderSatisCareer$SatisCareer == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderSatisCareer <- graphdf1genderSatisCareer

###Set variable order
graphdf1genderSatisCareer$SatisCareer <- factor(graphdf1genderSatisCareer$SatisCareer , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderSatisCareer) + 
  geom_bar(mapping = aes(x = Gender, fill = SatisCareer), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Managing complex projects

<br>

Column: MngCompProj
Data Frame: graphdf1genderMngCompProj
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderMngCompProj <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderMngCompProj<- graphdf1genderMngCompProj[!(graphdf1genderMngCompProj$MngCompProj == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderMngCompProj <- graphdf1genderMngCompProj

###Set variable order
graphdf1genderMngCompProj$MngCompProj <- factor(graphdf1genderMngCompProj$MngCompProj , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderMngCompProj) + 
  geom_bar(mapping = aes(x = Gender, fill = MngCompProj), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Developing a business plan

<br>

DevBusinessPlan
Data Frame: graphdf1genderDevBusinessPlan
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderDevBusinessPlan <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderDevBusinessPlan<- graphdf1genderDevBusinessPlan[!(graphdf1genderDevBusinessPlan$DevBusinessPlan == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderDevBusinessPlan <- graphdf1genderDevBusinessPlan

###Set variable order
graphdf1genderDevBusinessPlan$DevBusinessPlan <- factor(graphdf1genderDevBusinessPlan$DevBusinessPlan , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderDevBusinessPlan) + 
  geom_bar(mapping = aes(x = Gender, fill = DevBusinessPlan), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Managing people

<br>

Column: MngPeople
Data Frame: graphdf1genderMngPeople
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderMngPeople <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderMngPeople<- graphdf1genderMngPeople[!(graphdf1genderMngPeople$MngPeople == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderMngPeople <- graphdf1genderMngPeople

###Set variable order
graphdf1genderMngPeople$MngPeople <- factor(graphdf1genderMngPeople$MngPeople , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderMngPeople) + 
  geom_bar(mapping = aes(x = Gender, fill = MngPeople), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against Managing a large operational budget

<br>

Column: MngLargeBudget
Data Frame: graphdf1genderMngLargeBudget
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderMngLargeBudget <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderMngLargeBudget<- graphdf1genderMngLargeBudget[!(graphdf1genderMngLargeBudget$MngLargeBudget == "Unsure/Not applicable"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderMngLargeBudget <- graphdf1genderMngLargeBudget

###Set variable order
graphdf1genderMngLargeBudget$MngLargeBudget <- factor(graphdf1genderMngLargeBudget$MngLargeBudget , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well"))

##Plot
ggplot(data = graphdf1genderMngLargeBudget) + 
  geom_bar(mapping = aes(x = Gender, fill = MngLargeBudget), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against I feel that my programme is preparing me well for a research career

<br>

Column: FeelProgPrepResearch
Data Frame: graphdf1genderFeelProgPrepResearch
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderFeelProgPrepResearch <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderFeelProgPrepResearch<- graphdf1genderFeelProgPrepResearch[!(graphdf1genderFeelProgPrepResearch$FeelProgPrepResearch == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderFeelProgPrepResearch <- graphdf1genderFeelProgPrepResearch

###Set variable order
graphdf1genderFeelProgPrepResearch$FeelProgPrepResearch <- factor(graphdf1genderFeelProgPrepResearch$FeelProgPrepResearch , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdf1genderFeelProgPrepResearch) + 
  geom_bar(mapping = aes(x = Gender, fill = FeelProgPrepResearch), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against I feel that my programme is perparing me well for a non-research science-related career

<br>

Column: FeelProgPrepScience
Data Frame: graphdf1genderFeelProgPrepScience
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderFeelProgPrepScience <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderFeelProgPrepScience<- graphdf1genderFeelProgPrepScience[!(graphdf1genderFeelProgPrepScience$FeelProgPrepScience == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderFeelProgPrepScience <- graphdf1genderFeelProgPrepScience

###Set variable order
graphdf1genderFeelProgPrepScience$FeelProgPrepScience <- factor(graphdf1genderFeelProgPrepScience$FeelProgPrepScience , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdf1genderFeelProgPrepScience) + 
  geom_bar(mapping = aes(x = Gender, fill = FeelProgPrepScience), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

#### Gender Against I feel that my programme is preparing me well for a career that straddles both industry and academia

<br>

Column: FeelProgPrepMixIndAcad
Data Frame: graphdf1genderFeelProgPrepMixIndAcad
```{r}
###New data frame, to ensure there are no issues down the line
graphdf1genderFeelProgPrepMixIndAcad <- df
###Keep all values that are not containing "Unsure/Not applicable"
graphdf1genderFeelProgPrepMixIndAcad<- graphdf1genderFeelProgPrepMixIndAcad[!(graphdf1genderFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad == "I don't know"),]

###Refresh old graphdf1gender with data_new1 info
graphdf1genderFeelProgPrepMixIndAcad <- graphdf1genderFeelProgPrepMixIndAcad

###Set variable order
graphdf1genderFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad <- factor(graphdf1genderFeelProgPrepMixIndAcad$FeelProgPrepMixIndAcad , levels=c("Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

##Plot
ggplot(data = graphdf1genderFeelProgPrepMixIndAcad) + 
  geom_bar(mapping = aes(x = Gender, fill = FeelProgPrepMixIndAcad), position = "fill")+
  scale_colour_brewer(palette = "BrBg") +
  scale_fill_brewer(palette = "BrBG") +
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```






### Appendix: Misc Example Code Area

<br>

How to rename once
```{r}
###AV Script to rename one or multiples, same for multiples but just repeat first line till the end and second line once at the end. Both lines are required for a successful renaming and creation of a new data frame. I have no idea why.

#df14 <- names(df13)[1] <- "Collecting" 
#df14 <- df13

```

Basic plot
```{r}
#ggplot(data = df) + 
    ###actual plot bit
 # geom_bar(mapping = aes(x = Gender, fill = Collecting), position = "fill")+
    ###color
  #scale_colour_brewer(palette = "BrBg") +
   #scale_fill_brewer(palette = "BrBG") +
  ### Makes sure that the names/titles/labels do not overlap
     #scale_x_discrete(guide = guide_axis(n.dodge=2))
```

Creating new data frames by selecting only rows with a certain value
```{r}
#Possibly create new dataframes by row value
#df12Male <- df12[df12$'Gender' == 'Male (including trans male)',]
#df12Female <- df12[df12$'Gender' == 'Female (including trans female)',]
#df12GenderQueerandorNonBinary <- df12[df12$'Gender' == 'Gender queer / Non binary',]
```

```{r}

```

```{r}

```




This will be the bread and butter of this assignment. It looks beautiful. Waffle Graph, must have info input manually. Still beautiful.
```{r}
#parts <- c(`Un-breached\nUS Population` = (318 - 11 - 79), `Premera` = 11, `Anthem` = 79)

#waffle(
 # parts, rows = 8, size = 1,
  #colors = c("#969696", "#1879bf", "#009bda"), legend_pos = "bottom"

```












## Appendix: Misc Example Code Area

How to rename once
```{r}
###AV Script to rename one or multiples, same for multiples but just repeat first line till the end and second line once at the end. Both lines are required for a successful renaming and creation of a new data frame. I have no idea why.

#df14 <- names(df13)[1] <- "Collecting" 
#df14 <- df13

```

Basic plot
```{r}
#ggplot(data = df) + 
    ###actual plot bit
 # geom_bar(mapping = aes(x = Gender, fill = Collecting), position = "fill")+
    ###color
  #scale_colour_brewer(palette = "BrBg") +
   #scale_fill_brewer(palette = "BrBG") +
  ### Makes sure that the names/titles/labels do not overlap
     #scale_x_discrete(guide = guide_axis(n.dodge=2))
```

Creating new data frames by selecting only rows with a certain value
```{r}
#Possibly create new dataframes by row value
#df12Male <- df12[df12$'Gender' == 'Male (including trans male)',]
#df12Female <- df12[df12$'Gender' == 'Female (including trans female)',]
#df12GenderQueerandorNonBinary <- df12[df12$'Gender' == 'Gender queer / Non binary',]
```

Analysis that isn't working yet
```{r}
#lm1 <- lm(data = df, Collecting ~ Gender) # the model

#summary(lm1) # summarizes the output of the model
```

####Gender against Collecting Data 
first graph, not incredibly interesting and also hampered by small sample size of Gender Queer/Non Binary and Prefer Not To Say
```{r}

#groupedBarImmCollecting <- ggplot(data = dfImm) + 
 # geom_bar(mapping = aes(x = Immigration, fill = Collecting), position = "dodge")+
#  scale_colour_brewer(palette = "BrBG") +
 # scale_fill_brewer(palette = "BrBG") +
#  scale_x_discrete(guide = guide_axis(n.dodge=2))


#groupedBarGenderCollectingImm

```
A better proportional graph. This chunk also contains the code to reorder variables manually.
```{r}
#data_newImm <- dfImm
#dfImm <- data_newImm

#dfImm$Collecting <- factor(dfImm$Collecting , levels=c("Very badly", "Badly", "Neither well nor badly", "Well", "Very well", "Unsure/Not applicable"))

#data_newImm <- dfImm
#dfImm <- data_newImm


#ggplot(data = data_newImm) + 
#  geom_bar(mapping = aes(x = Immigration, fill = Collecting), position = "fill")+
#  scale_colour_brewer(palette = "BrBG") +
#  scale_fill_brewer(palette = "BrBG") +
#  scale_x_discrete(guide = guide_axis(n.dodge=2))

```

Analysis for Collecting Data Variable against Gender, Count and Proportion
```{r}
###Output A Table and dataframe, possible first step in analysis given grouping. difficult to say, would replace collecting with M, F, GQNB, as derived from dfM, dfF, dfGQNB, then combine, then analyze.
#Collecting <- table(df12['Collecting'])
#genderVsCollecting <- as.data.frame.array(Collecting)
#genderVsCollecting


###Proportional Analysis
#CollectingProportion <- as.data.frame(table(df12$Collecting)/length(df12$Collecting))
###Display Output
#CollectingProportion
```

```{r}

```

```{r}

```





