---
title: "CoreCode"
author: "ADMValverde"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Background:
This is the github post that lead me to the dataset
https://github.com/rfordatascience/tidytuesday/issues/153
This is the dataset
https://figshare.com/s/74a5ea79d76ad66a8af8
This is the course that I am writing this code for
https://data-science-methods.github.io/project/


Load in Libraries and Installations
```{r}
library(tidyverse)
library(readxl)
```


Load in dataset that I downloaded from the link above(and which I placed into a "data" folder within the project folder)
```{r}
dfog <- read_excel("data/Nature_PhD survey_Anon_v1.xlsx")
```


This is meant to ensure that it all was imported properly
```{r}
glimpse(dfog)
```
Just to check that the top has been preserved.
```{r}
head(dfog)
```


So there are alot of NA's here, I am removing those by combining bits that perhaps ought not have been separated out. The demographic data, for example, appears to have only one value per row(individual) and yet is scattered across multiple columns. I will combine Q58:1 to Q58.Am while excluding Q58:11, as that one is just specifying that a person is another ethnicity, which they then typed out by hand.
First, I will remove the column Q58:11, and then combine the aforementioned sections.
To remove Q58:11 I will have to rename it, as the ":" in the name causes issues in function"select".
```{r}
df1 <- dfog
df2 <- df1 #%>% dplyr::rename(delete = 259)
df3 <- df2 #%>% select(-delete)

```


In hindsight, why not just remove the top row and use the second row (the questions themselves) as the column identifier? That would make this easier, no?
```{r}
df4<-df3
names(df4) <- as.matrix(df4[1, ])
df4 <- df4[-1, ]
df4[] <- lapply(df4, function(x) type.convert(as.character(x)))
```


remove all columns where all values are NA
```{r}
df5 <- df4
df6a <- df5[ , colSums(is.na(df4)) < nrow(df4)]
```



All this to combine the demographic data

Before I do that, I have to rename columns that currently have the same name. I swear this dataset was meant to frustrate me. Also I have to rename column 117 in df6a, because the column name is blank. Not sure how the bottom bit works with attributing df6 to df6a after I declared df6, but it does. I tried it other ways and it didnt output a df6. comment out df6 <- df6a and test yourself if ya like.
I have now decided to use this path to rename all bits, because it wont work otherwise with dplyr's tools, only with base r.

```{r}
df6 <- df6a
df6 <- names(df6a)[117] <- "How much do you expect your PhD to improve your job prospects?"     ###AV Coulumn name/question is sourced from Nature_GradSurvey_Script2019_Final1.docx, named cause it was blank


###AV Rename all duplicates of "If other, please specify" and make unique
df6 <- names(df6a)[12] <- "specified1" 
df6 <- names(df6a)[16] <- "specified2" 
df6 <- names(df6a)[22] <- "specified3" 

df6 <- names(df6a)[34] <- "specified4" 
df6 <- names(df6a)[37] <- "specified5" 
df6 <- names(df6a)[54] <- "specified6" 
df6 <- names(df6a)[79] <- "specified7" 
df6 <- names(df6a)[89] <- "specified8"

df6 <- names(df6a)[104] <- "specified9" 
df6 <- names(df6a)[116] <- "specified10" 
df6 <- names(df6a)[139] <- "specified11" 
df6 <- names(df6a)[141] <- "specified12" 
df6 <- names(df6a)[146] <- "specified13" 

df6 <- names(df6a)[158] <- "specified14" 
df6 <- names(df6a)[173] <- "specified15" 
df6 <- names(df6a)[183] <- "specified16" 
df6 <- names(df6a)[191] <- "specified17" 
df6 <- names(df6a)[200] <- "specified18"

df6 <- names(df6a)[225] <- "specified19" 
df6 <- names(df6a)[233] <- "specified20" 
df6 <- names(df6a)[239] <- "specified21" 
df6 <- names(df6a)[255] <- "specified22" 
df6 <- names(df6a)[261] <- "specified23"



###AV Rename all duplicates of "What prompted you to study outside your country of upbringing" and make unique
df6 <- names(df6a)[23] <- "prompt to study outside country of upbringing1" 
df6 <- names(df6a)[24] <- "prompt to study outside country of upbringing2" 
df6 <- names(df6a)[25] <- "prompt to study outside country of upbringing3" 
df6 <- names(df6a)[26] <- "prompt to study outside country of upbringing4" 
df6 <- names(df6a)[27] <- "prompt to study outside country of upbringing5" 
df6 <- names(df6a)[28] <- "prompt to study outside country of upbringing6" 
df6 <- names(df6a)[29] <- "prompt to study outside country of upbringing7" 
df6 <- names(df6a)[30] <- "prompt to study outside country of upbringing8" 
df6 <- names(df6a)[31] <- "prompt to study outside country of upbringing9" 
df6 <- names(df6a)[32] <- "prompt to study outside country of upbringing10" 
df6 <- names(df6a)[33] <- "prompt to study outside country of upbringing11" 


###AV Rename all duplicates of "Who was the perpetrator(s)" and make unique
df6 <- names(df6a)[97] <-  "positionOfPerpetrator1" 
df6 <- names(df6a)[98] <-  "positionOfPerpetrator2" 
df6 <- names(df6a)[99] <-  "positionOfPerpetrator3" 
df6 <- names(df6a)[100] <- "positionOfPerpetrator4" 
df6 <- names(df6a)[101] <- "positionOfPerpetrator5" 
df6 <- names(df6a)[102] <- "positionOfPerpetrator6" 
df6 <- names(df6a)[103] <- "positionOfPerpetrator7" 


###AV Rename all duplicates of "Which of the following have you experienced?" and make unique
df6 <- names(df6a)[107] <- "experience1" 
df6 <- names(df6a)[108] <- "experience2" 
df6 <- names(df6a)[109] <- "experience3" 
df6 <- names(df6a)[110] <- "experience4" 
df6 <- names(df6a)[111] <- "experience5" 
df6 <- names(df6a)[112] <- "experience6" 
df6 <- names(df6a)[113] <- "experience7" 
df6 <- names(df6a)[114] <- "experience8" 
df6 <- names(df6a)[115] <- "experience9" 


###AV Rename all duplicates of "If you’re unlikely to pursue an academic research career, what are the main reasons??" and make unique
df6 <- names(df6a)[130] <- "reasonUnlikelyAcademicCarreerPursuit1" 
df6 <- names(df6a)[131] <- "reasonUnlikelyAcademicCarreerPursuit2" 
df6 <- names(df6a)[132] <- "reasonUnlikelyAcademicCarreerPursuit3" 
df6 <- names(df6a)[133] <- "reasonUnlikelyAcademicCarreerPursuit4" 
df6 <- names(df6a)[134] <- "reasonUnlikelyAcademicCarreerPursuit5" 
df6 <- names(df6a)[135] <- "reasonUnlikelyAcademicCarreerPursuit6" 
df6 <- names(df6a)[136] <- "reasonUnlikelyAcademicCarreerPursuit7" 
df6 <- names(df6a)[137] <- "reasonUnlikelyAcademicCarreerPursuit8" 
df6 <- names(df6a)[138] <- "reasonUnlikelyAcademicCarreerPursuit9" 

###AV Rename all duplicates of "How did you arrive at your current career decision? Plea..." and make unique
df6 <- names(df6a)[147] <- "HowArriveAtCareerDecision1" 
df6 <- names(df6a)[148] <- "HowArriveAtCareerDecision2" 
df6 <- names(df6a)[149] <- "HowArriveAtCareerDecision3" 
df6 <- names(df6a)[151] <- "HowArriveAtCareerDecision4" 
df6 <- names(df6a)[152] <- "HowArriveAtCareerDecision5" 
df6 <- names(df6a)[153] <- "HowArriveAtCareerDecision6" 
df6 <- names(df6a)[154] <- "HowArriveAtCareerDecision7" 
df6 <- names(df6a)[155] <- "HowArriveAtCareerDecision8" 
df6 <- names(df6a)[156] <- "HowArriveAtCareerDecision9" 
df6 <- names(df6a)[157] <- "HowArriveAtCareerDecision10" 

###AV Rename all duplicates of "How do you learn about available career opportunities that are beyond academia?" and make unique
df6 <- names(df6a)[159] <- "HowLearnCareerNotAcademia1" 
df6 <- names(df6a)[160] <- "HowLearnCareerNotAcademia2" 
df6 <- names(df6a)[161] <- "HowLearnCareerNotAcademia3" 
df6 <- names(df6a)[162] <- "HowLearnCareerNotAcademia4" 
df6 <- names(df6a)[163] <- "HowLearnCareerNotAcademia5" 
df6 <- names(df6a)[164] <- "HowLearnCareerNotAcademia6" 
df6 <- names(df6a)[165] <- "HowLearnCareerNotAcademia7" 
df6 <- names(df6a)[166] <- "HowLearnCareerNotAcademia8" 
df6 <- names(df6a)[167] <- "HowLearnCareerNotAcademia9" 
df6 <- names(df6a)[168] <- "HowLearnCareerNotAcademia10" 
df6 <- names(df6a)[169] <- "HowLearnCareerNotAcademia11" 
df6 <- names(df6a)[170] <- "HowLearnCareerNotAcademia12" 
df6 <- names(df6a)[171] <- "HowLearnCareerNotAcademia13" 
df6 <- names(df6a)[172] <- "HowLearnCareerNotAcademia14" 

###AV Rename all duplicates of "Which of the following 3 things would you say are the most difficult for PhD students in your discipline?" and make unique
df6 <- names(df6a)[174] <- "DifficultInDiscipline1" 
df6 <- names(df6a)[175] <- "DifficultInDiscipline2" 
df6 <- names(df6a)[176] <- "DifficultInDiscipline3" 
df6 <- names(df6a)[177] <- "DifficultInDiscipline4" 
df6 <- names(df6a)[178] <- "DifficultInDiscipline5" 
df6 <- names(df6a)[179] <- "DifficultInDiscipline6" 
df6 <- names(df6a)[180] <- "DifficultInDiscipline7" 
df6 <- names(df6a)[181] <- "DifficultInDiscipline8" 
df6 <- names(df6a)[182] <- "DifficultInDiscipline9" 


###AV Rename all duplicates of "Which of the following would you say are the most difficult for PhD students in the country where you are studying?" and make unique
df6 <- names(df6a)[184] <- "DifficultInCountry1" 
df6 <- names(df6a)[185] <- "DifficultInCountry2" 
df6 <- names(df6a)[186] <- "DifficultInCountry3" 
df6 <- names(df6a)[187] <- "DifficultInCountry4" 
df6 <- names(df6a)[188] <- "DifficultInCountry5" 
df6 <- names(df6a)[189] <- "DifficultInCountry6" 
df6 <- names(df6a)[190] <- "DifficultInCountry7" 

###AV Rename all duplicates of "Which of the following resources do you think PhD students need the most in order to establish a satisfying career?" and make unique
df6 <- names(df6a)[192] <- "ResourcesForSatisfyingCareer1" 
df6 <- names(df6a)[193] <- "ResourcesForSatisfyingCareer2" 
df6 <- names(df6a)[194] <- "ResourcesForSatisfyingCareer3" 
df6 <- names(df6a)[195] <- "ResourcesForSatisfyingCareer4" 
df6 <- names(df6a)[196] <- "ResourcesForSatisfyingCareer5" 

df6 <- names(df6a)[197] <- "ResourcesForSatisfyingCareer6" 
df6 <- names(df6a)[198] <- "ResourcesForSatisfyingCareer7" 
df6 <- names(df6a)[199] <- "ResourcesForSatisfyingCareer8" 

###AV Rename all duplicates of "Which, if any, of the following activities have you done to advance your career?" and make unique
df6 <- names(df6a)[217] <- "ActivitiesToAdvanceCareer1" 
df6 <- names(df6a)[218] <- "ActivitiesToAdvanceCareer2" 
df6 <- names(df6a)[219] <- "ActivitiesToAdvanceCareer3" 
df6 <- names(df6a)[220] <- "ActivitiesToAdvanceCareer4" 
df6 <- names(df6a)[221] <- "ActivitiesToAdvanceCareer5" 

df6 <- names(df6a)[222] <- "ActivitiesToAdvanceCareer6" 
df6 <- names(df6a)[223] <- "ActivitiesToAdvanceCareer7" 
df6 <- names(df6a)[224] <- "ActivitiesToAdvanceCareer8" 


###AV Rename all duplicates of "Which of the following social media networks have you used to build your professional network" and make unique
df6 <- names(df6a)[226] <- "SocialMediaToBuildNetwork1" 
df6 <- names(df6a)[227] <- "SocialMediaToBuildNetwork2" 
df6 <- names(df6a)[228] <- "SocialMediaToBuildNetwork3" 
df6 <- names(df6a)[229] <- "SocialMediaToBuildNetwork4" 
df6 <- names(df6a)[230] <- "SocialMediaToBuildNetwork5" 
df6 <- names(df6a)[231] <- "SocialMediaToBuildNetwork6" 
df6 <- names(df6a)[232] <- "SocialMediaToBuildNetwork7" 

###AV Rename all duplicates of "What would you do differently right now if you were starting your programme?" and make unique
df6 <- names(df6a)[234] <- "DoDifferently1" 
df6 <- names(df6a)[235] <- "DoDifferently2" 
df6 <- names(df6a)[236] <- "DoDifferently3" 
df6 <- names(df6a)[237] <- "DoDifferently4" 
df6 <- names(df6a)[238] <- "DoDifferently5" 


###AV Rename all duplicates of "Which of the following best describes you?" and make unique
df6 <- names(df6a)[243] <- "BestDescribes1" 
df6 <- names(df6a)[244] <- "BestDescribes2" 
df6 <- names(df6a)[245] <- "BestDescribes3" 
df6 <- names(df6a)[246] <- "BestDescribes4" 
df6 <- names(df6a)[247] <- "BestDescribes5" 

df6 <- names(df6a)[248] <- "BestDescribes6" 
df6 <- names(df6a)[249] <- "BestDescribes7" 
df6 <- names(df6a)[250] <- "BestDescribes8" 
df6 <- names(df6a)[251] <- "BestDescribes9" 
df6 <- names(df6a)[252] <- "BestDescribes10"

df6 <- names(df6a)[253] <- "BestDescribes11" 
df6 <- names(df6a)[254] <- "BestDescribes12"


###AV Rename all duplicates of "Do you have any caring responsibilities" and make unique
df6 <- names(df6a)[256] <- "CaringResponsibilities1" 
df6 <- names(df6a)[257] <- "CaringResponsibilities2" 
df6 <- names(df6a)[258] <- "CaringResponsibilities3" 
df6 <- names(df6a)[259] <- "CaringResponsibilities4" 
df6 <- names(df6a)[260] <- "CaringResponsibilities5" 



#df6 <- names(df5)[20] <- "delete2"  
#df6 <- names(df6a)[] <- "" 
df6 <- df6a

#code adapted from https://www.statology.org/how-to-rename-data-frame-columns-in-r/ and https://www.sharpsightlabs.com/blog/rename-columns-in-r/
#df6 <- names(df5) <- c("miles_gallon", "cylinders", "display", "horsepower")

###AV This bottom bit told me what I am missing to rename and make not identical
###rename(df6, combine1 = 150)


###df6 <- rename(df5, xyz=1) ###AV Didnt Work. Will use something other than rename

###df6 %>% unite("ethnicity", 251:259, remove = FALSE)

###AV Template for above
####AV Rename all duplicates of "" and make unique
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 
#df6 <- names(df6a)[] <- "" 

###Finished Product: df7
df7 <- df6

```



actually combine demographic data

```{r}
df8 <- unite(df7, "ethnicityGroupedOther",  243:254, remove = FALSE, na.rm = TRUE)
#df7 %>% unite("ethnicityOtherWriteInIncluded", 2,remove= FALSE) specified22 is variable that has the write in ethnicity data
df9 <- unite(df8, "ethnicityOtherWriteInNotYetIncluded", 244:252, remove = FALSE, na.rm = TRUE)
###AV Ensure that all NA values remain as NA, as the above unite processes seem to convert NA to blanks after uniting. Comment out the 2 lines below to confirm.
df10 <- df9 
df10[df10 == ""] <- NA 
###AV finally combine them all
df11 <- unite(df10, "ethnicityOtherWriteInIncluded", c('ethnicityOtherWriteInNotYetIncluded', 'specified22') , remove = FALSE, na.rm = TRUE)
```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```


```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```


